paper

### 2024-09-27 inst/extdata/paperdata/paper.qmd
.

```{r}
{r}
# Load necessary packages
library(LimROTS)
library(parallel)
library(SummarizedExperiment)
# Load the dataset
data("proteogenomicPD")
print(soma)

@@

```{r}
plot(limrots.result2$q_values)
hist(limrots.result2$q_values)
hist(limrots.result2$q_values$qvalues)
hist(limrots.result2$FDR)

@@

# Set metadata and formula for LimROTS analysis
meta.info <- names(soma0.5@colData@listData)
B <- 1000  # Number of bootstrap samples
K <- dim(soma0.5)[1]/4  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "group_comp"
formula.str <- "~ 0 + group_comp + gender + AGE + CNO + pc1 + pc2 + pc3 + pc4"  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled

soma0.5@colData@listData[["CNO"]] <- paste0("CNO" , soma0.5@colData@listData[["CNO"]])

soma0.5@colData@listData[["CNO"]] <- as.factor(soma0.5@colData@listData[["CNO"]])

@@

>>>>

# Load necessary packages
library(LimROTS)
library(parallel)
library(SummarizedExperiment)
# Load the dataset
data("proteogenomicPD")
print(soma)

@@

saveRDS(limrots.result, "D:/LimROTS/inst/extdata/paperdata/Soma.noPCs.LimROTS.rds")

@@

# Set metadata and formula for LimROTS analysis
meta.info <- names(soma0.5@colData@listData)
B <- 1000  # Number of bootstrap samples
K <- dim(soma0.5)[1]/4  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "group_comp"
formula.str <- "~ 0 + group_comp + gender + AGE + CNO"  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled

@@

saveRDS(soma0.5, "D:/LimROTS/inst/extdata/paperdata/Soma0.5.noPCs.LimROTS.rds")
